---
title: "DataFrame"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataframe from column vectors
A data frame is a collection of columns, each of which corresponds to an observed
variable (in the statistical sense, not the programming sense). If your data is already
organized into columns, then it’s easy to build a data frame.
The data.frame function can construct a data frame from vectors, where each vector is
one observed variable. Suppose you have two numeric predictor variables, one categorical predictor variable, and one response variable. The data.frame function can create a data frame from your vectors:

```{r }
names <- c("kedar","shyam","mohan","geeta","seema","priya")
ages <- c(23,22,21,22,23,23)
height <- c(165,170,167,160,164,166)
has_specs <- c("yes","no","no","yes","no","yes")
```

```{r }
data.frame(names,ages)
```

```{r }
data.frame(names,height)
```

```{r }
data.frame(ages,height)
```


```{r }
data.frame(height,has_specs)
```

```{r }
data.frame(names,ages,height,has_specs)
```


```{r }
data.frame(Name=names,Age=ages,Height=height,Glasses=has_specs)
```

Alternatively, your data may be organized into vectors but those vectors are held in a
list, not individual program variables, like this:

```{r }
list(names,ages,height,has_specs)
```




```{r }
data.frame(list(Name=names,Age=ages,Height=height,Glasses=has_specs))
```


## Dataframe from rows vectors

Data often arrives as a collection of observations. Each observation is a record or tuple
that contains several values, one for each observed variable. Such data is organized by
initializing a Data Frame from Row Data observation, not by variable. In other words, you are given rows one at a time rather than columns one at a time.


```{r }
obs <- list(
  c("Name"="kedar","Age"=23,"Height"=165,"Glasses"="yes"),
  c("Name"="shyam","Age"=22,"Height"=170,"Glasses"="no"),
  c("Name"="mohan","Age"=21,"Height"=167,"Glasses"="no")
)
```



```{r }
obs[[1]]
```

```{r }
rbind(obs[[1]],obs[[2]])
```

We want to bind together every observation, not just the first two, so we tap into the
vector processing of R. The do.call function will expand obs into one, long argument
list and call rbind with that long argument list:

```{r }
 do.call(rbind,obs)
```



## appending row to dataframe

```{r }
data=data.frame(list(Name=names,Age=ages,Height=height,Glasses=has_specs))
new_obs<-data.frame("Name"="Anthony","Age"=26,"Height"=165,"Glasses"="yes")
rbind(data,new_obs)
```


## select columns by position

```{r }
data[[2]]
```

```{r }
data[2]
```

```{r }
data[c(2,3)]
```

```{r }
data[,c(2,3)]
```

```{r }
data[,2]
```

## select columns by name

```{r }
data[["Age"]]
```

```{r }
data["Age"]
```

```{r }
data[,"Age"]
```

```{r }
data[,c("Age","Height")]
```


## subset function

```{r }
subset(data,select=Age)
```

```{r }
subset(data,subset=(Age<23))
```

## change names of dataframe columns

```{r }
colnames(data)=c("patient","p_age","p_height","p_glasses")
data
```

## matrix to dataframe
```{r }
mat=matrix(1:9, byrow = TRUE, nrow = 3)
mat_df=as.data.frame(mat)
mat_df
```


```{r }
colnames(mat_df)=c("col1","col2","col3")
mat_df
```

## combine two dataframes by column
```{r }
cbind(subset(data,subset=(p_age<23)),
      mat_df)

```

## combine on specific column

```{r }
born<-rbind(data.frame("name"="mohan",
                 "place_b"="shirdi",
                 "year_b"=1959),
            data.frame("name"="girija",
                 "place_b"="pune",
                 "year_b"=1950)
            
)

dead<-rbind(data.frame("name"="mohan",
                 "place_d"="shirdi",
                 "year_d"=2018),
            data.frame("name"="girija",
                 "place_d"="pune",
                 "year_d"=2000)
)
            

```


```{r }
born        

```




```{r }
dead        

```

```{r }
cbind(born,dead)
```


```{r }
merge(born,dead,by="name")
```


```{r }
born        

```


```{r }
born        

```


