---
title: "data_frame_question"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create an empty data frame. 

```{r }
df=data.frame()
```

2. Create a data frame from four given vectors. 

```{r }
vec1=
vec2=

df=data.frame()
```

3. Get the structure of a given data frame.
```{r }
str(i)
```


4. Write a R program to get the statistical summary and nature of the data of a given data frame. Go to the editor
Click me to see the sample solution

5. Write a R program to extract specific column from a data frame using column name. Go to the editor
Click me to see the sample solution

6. Write a R program to extract first two rows from a given data frame. Go to the editor
Click me to see the sample solution

7. Write a R program to extract 3rd and 5th rows with 1st and 3rd columns from a given data frame. Go to the editor
Click me to see the sample solution

8. Write a R program to add a new column in a given data frame. Go to the editor
Click me to see the sample solution

9. Write a R program to add new row(s) to an existing data frame. Go to the editor
Click me to see the sample solution

10. Write a R program to drop column(s) by name from a given data frame. Go to the editor
Click me to see the sample solution

11. Write a R program to drop row(s) by number from a given data frame. Go to the editor
Click me to see the sample solution

12. Write a R program to sort a given data frame by multiple column(s). Go to the editor
Click me to see the sample solution

13. Write a R program to create inner, outer, left, right join(merge) from given two data frames. Go to the editor
Click me to see the sample solution

14. Write a R program to replace NA values with 3 in a given data frame. Go to the editor
Click me to see the sample solution

15. Write a R program to change a column name of a given data frame. Go to the editor
Click me to see the sample solution

16. Write a R program to change more than one column name of a given data frame. Go to the editor
Click me to see the sample solution

17. Write a R program to select some random rows from a given data frame. Go to the editor
Click me to see the sample solution

18. Write a R program to reorder an given data frame by column name. Go to the editor
Click me to see the sample solution

19. Write a R program to compare two data frames to find the elements in first data frame that are not present in second data frame. Go to the editor
Click me to see the sample solution

20. Write a R program to find elements which are present in two given data frames. Go to the editor
Click me to see the sample solution

21. Write a R program to find elements come only once that are common to both given data frames. Go to the editor
Click me to see the sample solution

22. Write a R program to save the information of a data frame in a file and display the information of the file. Go to the editor
Click me to see the sample solution

23. Write a R program to count the number of NA values in a data frame column. Go to the editor
Click me to see the sample solution

24. Write a R program to create a data frame using two given vectors and display the duplicated elements and unique rows of the said data frame. Go to the editor
Click me to see the sample solution

25. Write a R program to call the (built-in) dataset airquality. Check whether it is a data frame or not? Order the entire data frame by the first and second column. Go to the editor
Click me to see the sample solution

26. Write a R program to call the (built-in) dataset airquality. Remove the variables 'Solar.R' and 'Wind' and display the data frame. Go to the editor
Click me to see the sample solution

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
