---
title: "factors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In R, each possible value of a categorical variable is called a level. A vector of levels is
called a factor. Factors fit very cleanly into the vector orientation of R, and they are
used in powerful ways for processing data and building statistical models.
Most of the time, converting your categorical data into a factor is a simple matter of
calling the factor function, which identifies the distinct levels of the categorical data
and packs them into a factor:

```{r }
f <- factor(c("Win","Win","Lose","Tie","Win","Lose"))
```

Notice that when we printed the factor, f, R did not put quotes around the values. They
are levels, not strings. Also notice that when we printed the factor, R also displayed the
distinct levels below the factor.
If your vector contains only a subset of all the possible levels, then R will have an
incomplete picture of the possible levels. Suppose you have a string-valued variable
wday that gives the day of the week on which your data was observed:

```{r }
f <- factor(c("wed","thu","mon"))
```



```{r }
days=c("Wed","Thu","Mon")
f <- factor(days)
f
```


```{r }
 f <- factor(days, c("Mon","Tue","Wed","Thu","Fri"))
f
```
Now R understands that f is a factor with five possible levels. It knows their correct
order, too. It originally put Thursday before Tuesday because it assumes alphabetical
order by default.† The explicit second argument defines the correct order.
In many situations it is not necessary to call factor explicitly. When an R function
requires a factor, it usually converts your data to a factor automatically. The table
function, for instance, works only on factors, so it routinely converts its inputs to factors
without asking. You must explicitly create a factor variable when you want to specify
the full set of levels or when you want to control the ordering of levels.

