---
title: "List"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## what would happen if you combine vectors of different class 

```{r }

vec <- c(1,2,3)
char_vec <- c("R", "Rstudio", "Github")
logic_vec <- c(TRUE, FALSE, TRUE, FALSE)
out_list <- c(vec, char_vec, logic_vec)
out_list
class(out_list)
```


## Try it in list

```{r }

vec <- c(1,2,3)
char_vec <- c("R", "Rstudio", "Github")
logic_vec <- c(TRUE, FALSE, TRUE, FALSE)
out_list <- list(vec, char_vec, logic_vec)
out_list
#class(out_list)
#str(out_list)
```

## access elements

```{r }

out_list[1]
out_list[[1]][1]
```


## check class

```{r }

class(out_list[[1]])

```


## give names

```{r }
names(out_list) <- c("num", "char", "logic")
out_list
```

## access elements by names

```{r }

out_list$num
```


## add element to end of list

```{r }
out_list[4] <- "New_element"

```

## remove the last element

```{r }

out_list[4] <- NULL
```



## merge two lists

```{r }
num_list <- list(c(1,2,3,4,5) )    
day_list <- list(c("Mon","Tue","Wed", "Thurs", "Fri"))
merge_list <- c(num_list, day_list)
merge_list
```



## convert list to vector

```{r }
int_list <- list(1:5)     
int_list2 <- list(10:14)

vec1 <- unlist(int_list)
vec2 <- unlist(int_list2)

```


## matrix example with list

```{r }
Seinfeld <- c(13, 11)
Friends <- c(53, 49)
Office <- c(40, 35)

pop_index <- c(Seinfeld, Friends, Office)

tv_matrix <- matrix(pop_index, byrow = TRUE, nrow = 3,
                    dimnames = list(c("Seinfeld", "Friends", "Office"),
                                    c("year_2018", "year_2019")))

tv_matrix
```

> ### Challenge
>
>
> 1. make a list that contains - \n
> a. names of your favourite books or films,
> b. how many hours do you and 3 of your friends sleep?
> c. answer to these questions -
> I. Do you like cats?
> II. Do you like dogs?
> III. Do you like rain?
> IV. Do you hate winters?

