---
title: "Matrices"
output: html_document
---
# matrices
```{r }
vector1 <- c(2,9,3)
vector2 <- c(10,16,17,13,11,15)
vector2
```

```{r }
result <- array(c(vector1,vector2),dim = c(3,3,2))
result
```

```{r }
vector1 <- c(2,9,6)
vector2 <- c(10,15,13,16,11,12)
column.names <- c("COL1","COL2","COL3")
row.names <- c("ROW1","ROW2","ROW3")
matrix.names <- c("Matrix1","Matrix2")
```

```{r }
result <- array(c(vector1,vector2),dim = c(3,3,2),dimnames = list(row.names,column.names,
  matrix.names))
#print(result)
#print(result[3,,2])
#print(result[1,3,1])

matrix1 <- result[,,1]
matrix2 <- result[,,2]

matrix1
```
```{r }
vector1 <- c(1,2,3)
vector2 <- c(3,4,5,6,7,8)


array1 <- array(c(vector1,vector2),dim = c(3,3,2))

vector3 <- c(3,2,1)
vector4 <- c(8,7,6,5,4,3)
array2 <- array(c(vector1,vector2),dim = c(3,3,2))

matrix1 <- array1[,,2]
matrix2 <- array2[,,2]

result <- matrix1+matrix2
print(result)

```

## What's a matrix?
In R, a matrix is a collection of elements of the same data type (numeric, character, or logical) arranged into a fixed number of rows and columns. Since you are only working with rows and columns, a matrix is called two-dimensional.

You can construct a matrix in R with the matrix() function. Consider the following example:

```{r }
matrix(1:9, byrow = TRUE, nrow = 3)
```



```{r , echo=T}
A = matrix( 
   c(2, 4, 3, 1, 5, 7), # the data elements 
   nrow=2,              # number of rows 
   ncol=3,              # number of columns 
   byrow = TRUE)        # fill matrix by rows 
A
```



An element at the mth row, nth column of A can be accessed by the expression A[m, n].

```{r , echo=T}
 A[2, 3]
```

The entire mth row A can be extracted as A[m, ].

```{r , echo=T}
 A[2, ] 
```

Similarly, the entire nth column A can be extracted as A[ ,n].

```{r , echo=T}
A[ ,3] 
```

We can also extract more than one rows or columns at a time.

```{r , echo=T}
A[ ,c(1,3)] 
```


```{r , echo=T}
A[ ,3] 
```



## Some matrix fun 

### Popularity of TV series


```{r }
Seinfeld <- c(13, 11)
Friends <- c(53, 49)
Office <- c(40, 35)
```

### Create popularity vector

```{r }
pop_index <- c(Seinfeld, Friends, Office)
```

### construct the TV matrix
```{r }
tv_matrix <- matrix(pop_index, byrow = TRUE, nrow = 3)

```

```{r }
tv_matrix 

```


### name the TV matrix

make two vectors
```{r }
year <- c("year_2018", "year_2019")
titles <- c("Seinfeld", "Friends", "Office")

```


```{r }
# Name the columns with region
colnames(tv_matrix) <- year

# Name the rows with titles
rownames(tv_matrix) <- titles
```

```{r }
tv_matrix
```

## operation on matrix

Difference
```{r }
tv_matrix[1,1]-tv_matrix[1,2]
```



> ### Challenge
>
>
> * Perform 5 operations on this matrix.




```{r }
A=matrix(1:9, byrow = TRUE, nrow = 3)
B=matrix(c(5,73,54,2,5,2,3,4,9), byrow = TRUE, nrow = 3)
  
```


```{r }
A
  
```



```{r }
B
  
```


Matrix transposition of A

```{r }
t(A)
  
```

Matrix multiplication of A and B

```{r }
A*B
  
```

```{r }
A%*%B
  
```

Matrix inverse of B

```{r }
solve(B)
  
```

An n-by-n diagonal (identity) matrix

```{r }
diag(10)
  
```


```{r }
diag(A)
  
```

